R Notebook

### 2017-05-18 manuscript/draft.Rmd
numbers for mistnet coverage

In general, the models produced confidence intervals that were too narrow,
indicating overconfident predictions. Of these, the random forest-based SDM
stack was the most overconfident, as discussed above. As one might expect,
correcting for observer differences improved the coverage of most models' 95%
intervals. Interestingly, this effect was very small for mistnet, which seems to
indicate that its latent variables were already accounting for observer-based
uncertainty. The "naive" model was the only model whose confidence intervals
were too wide (Figure 3), which can be attributed to the rapid rate at which
these intervals expand as the time lag increases (Figure 1).

>>>>

In general, the models produced confidence intervals that were too narrow,
indicating overconfident predictions. Of these, the random forest-based SDM
stack was the most overconfident, as discussed above. As one might expect,
correcting for observer differences improved the coverage of most models' 95%
intervals. Interestingly, this effect was very small for mistnet (its
coverage only improved from 92% to 93%), which seems to indicate that its
latent variables were already accounting for observer-related uncertainty. 
The "naive" model was the only model whose confidence intervals were too wide
(Figure 3), which can be attributed to the rapid rate at which
these intervals expand as the time lag increases (Figure 1).
